Transfer Learning in Multimodal Compositional and Relational Reasoning

### 2019-11-15 cvpr_submission/experiments.tex
Slight rephrasing of last experiments subsection to respect page limit.

First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
The former saw an accuracy jump from 68.6\% by training on samples from that family alone
to 97.0\% when training on all samples. To further emphasize this behavior, notice that 
just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
In hindsight, this is not surprising as the questions in \textbf{Compare} are composed
of fragments of the questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
is a slight loss incurred by including everything. As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%). To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

@@

The final set of experiments we consider is related to feature transfer.
The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color attributes.
The colors are partitioned into two complementary families: 
Gray, Blue, Brown and Yellow in Family A and Red, Green, Purple, Cyan in Family B. 
The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
the spheres can take any color. This is summarized in~\cref{tab:cogent_conditions}. 
If we consider the input domain to be the set of objects with all attributes values, both sets differ by the data distribution they are sampled from. We thus consider 2 experiments with SAMNet trained on CoGenT-A: A direct generalization test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following the procedure of~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}). The results are available in~\cref{fig:CoGenT-B-results}.

>>>>

First, notice that for each of the \textbf{Basic} and \textbf{Obj-Attr} task families, the accuracy is near-perfect in all cases, suggesting that each contains the most primitive of tasks and therefore do not benefit from training with other task families.
With \textbf{Spatial}, we see a small improvement showing that there is some benefit due to joint training with other task families.
Two groups that demonstrated a huge improvement of more than 25 points are \textbf{Compare} and \textbf{Cognitive}.
The former saw an accuracy jump from 68.6\% by training on samples from that family alone
to 97.0\% when training on all samples. To further emphasize this behavior, notice that 
just joining \textbf{Compare} with \textbf{Obj-Attr} and \textbf{Basic} already causes a significant accuracy jump to 92.3\%. 
In hindsight, this is not surprising, as the questions in \textbf{Compare} are composed
of fragments of questions given by \textbf{Basic} and \textbf{Obj-Attr}, and therefore can leverage the reasoning strategies developed there to reason about questions in \textbf{Compare}.
Lastly, for the \textbf{Spatial} family, we again see the benefits of joint training with all questions (68.6\% to 95.7\%) but in this case there
is a slight loss incurred by including everything. As seen in the figure, just jointly training with \textbf{Spatial} alone is sufficient to get a boost in accuracy (97.1\%). To summarize, while joint training helps, one needs to determine how much of correlation is present with the other tasks.

@@

The final set of experiments we consider is related to feature transfer.
The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color attributes.
The colors are partitioned into two complementary families: 
Gray, Blue, Brown and Yellow in Family A and Red, Green, Purple, Cyan in Family B. 
The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
the spheres can take any color (See~\cref{tab:cogent_conditions}). 
Considering the input domain to be the set of objects with all attributes values, both sets differ by their marginal distributions $P_S$ and $P_T$. We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}). The results are available in~\cref{fig:CoGenT-B-results}.
